Extended Data

### 2021-12-03 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd
@teixeirak rdendrom functions were used, not the package as a whole because it wasn't available on CRAN.  Climpact is an R package or a separate software, I used the separate software. We should probably clarify this throughout the paper. Other than that versions look good

# Code Availability Statement {-#Code}
Data were analysed in the open source statistical software R (version 4.0).
We used packages *Rdendrom* (https://github.com/seanmcm/RDendrom/), *climwin* v.1.2.3 (https://cran.r-project.org/web/packages/climwin/index.html), *climpact* (see www.climpact-sci.org)[@benestad_empiricalstatistical_2008], *dplR* **version###**, and *bootRes* **version###**. 
All custom code is available through the EcoClimlab GitHub repository (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI: [TBD]).

>>>>

# Code Availability Statement {-#Code}
Data were analysed in the open source statistical software R (version 4.0).
We used packages *Rdendrom* (https://github.com/seanmcm/RDendrom/), *climwin* v.1.2.3 (https://cran.r-project.org/web/packages/climwin/index.html), *climpact* (see www.climpact-sci.org)[@benestad_empiricalstatistical_2008], *dplR* v.1.0.2, and *bootRes* v1.2.4. 
All custom code is available through the EcoClimlab GitHub repository (https://github.com/EcoClimLab/growth_phenology) and archived in Zenodo (DOI: [TBD]).
